%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications supplement for Anthropic applications
% Compile: make supplement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist{nosep}

\begin{document}

\begin{center}
{\LARGE Dr. Julia Hasty}\\[4pt]
{\large Publications, Patents, and Presentations}\\[4pt]
\href{mailto:julia.hasty@gmail.com}{julia.hasty@gmail.com} |
\href{https://www.linkedin.com/in/dr-jay/}{linkedin.com/in/dr-jay}
\end{center}

\section*{Patents}
\begin{itemize}
\item US Patent 8,829,695 --- Compact gasifier-genset architecture (2017)
\item US Patent 9,476,352 --- Compact gasifier-genset architecture (2017)
\end{itemize}

\section*{Journal Publications}
\begin{itemize}
\item ``Effective landfill gas management strategies for methane control and reuse technology.'' \textit{Journal of Renewable and Sustainable Energy}, AIP (2015).
\item ``Catalytic Synthesis of Mixed Alcohols Mediated with Nano-Molybdenum Disulfide Microemulsions.'' \textit{Fuel} (2016).
\end{itemize}

\section*{Selected Presentations}
\begin{itemize}
\item ``A Fixation with Nitrogen --- Greenhouse Gas Emissions from Agriculture.'' Oral presentation, COP21 Regenerative Agriculture \& Land Use Workshop (co-organized by Kiss the Ground, Project Drawdown, and Regeneration International), Paris, France (2015).
\item ``Conversion of Biomass-derived Synthesis Gas to Mixed Alcohols Catalyzed by Nano-sized Molybdenum Disulfide.'' 8th Annual NYS Biotechnology Symposium (2016).
\item ``Biomass Gasification Technologies.'' Oral presentation, Advanced Energy Conference, Albany, NY (2014).
\item ``Synthesis of Mixed Alcohols From Biomass Using Slurried Nano-Sized Metal Particles.'' Poster, AIChE Annual Meeting, San Francisco, CA (2013).
\item ``Upgrading of Biomass-derived Bio-oil to Drop-In Replacement Renewable Hydrocarbon Fuels.'' NSF-CBERD Annual Meeting, Denver, CO (2011).
\item ``Biomass to Biofuel: Combined Heat, Power, Fuel \& Fertilizer.'' West Coast Convergence for Climate Action, Eugene, OR (2008).
\item ``Synthesis \& Characterization of Novel Carbon Based Solid Acid Catalysts for use in Biodiesel Production.'' Blue Ridge ACS Regional Meeting, Radford, VA (2006).
\end{itemize}

\section*{Awards}
\begin{itemize}
\item Winner, 2018 Water Abundance XPrize (SkySource)
\item NSF grant awards (ALL Power Labs, CPWater Tech)
\item USAID grant --- Liberia electrification, 250 homes during Ebola outbreak
\item New York State innovation award (CPWater Tech)
\item PowerBridge New York accelerator cohort (NanoSulf)
\end{itemize}

\end{document}
